```{r setup, include=FALSE}
library(readr)
library(stringr)
library(knitr)
library(htmltools)
opts_chunk$set(echo = FALSE, warning = FALSE, 
               message = FALSE, fig.align = "center")
```

```{r read_in_metadata}
cran_meta <- read_csv("metadata/cran.csv")
github_meta <- read_csv("metadata/github.csv")
cran_preview_html <- sub('[.][^.]+$', '', list.files("outputs/html")) %>%
  str_split("-")

```

<a href="https://github.com/rmdtemplates/rmdtemplates.github.io" class="github-corner"><svg width="50" height="50" viewBox="0 0 250 250" style="fill:#fff; color:#121212; position: absolute; top: 0; border: 0; right: 0; z-index: 2000;"><path d="M0,0 L115,115 L130,115 L142,142 L250,250 L250,0 Z"></path><path d="M128.3,109.0 C113.8,99.7 119.0,89.6 119.0,89.6 C122.0,82.7 120.5,78.6 120.5,78.6 C119.2,72.0 123.4,76.3 123.4,76.3 C127.3,80.9 125.5,87.3 125.5,87.3 C122.9,97.6 130.6,101.9 134.4,103.2" fill="currentColor" style="transform-origin: 130px 106px;" class="octo-arm"></path><path d="M115.0,115.0 C114.9,115.1 118.7,116.5 119.8,115.4 L133.7,101.6 C136.9,99.2 139.9,98.4 142.2,98.6 C133.8,88.0 127.5,74.4 143.8,58.0 C148.5,53.4 154.0,51.2 159.7,51.0 C160.3,49.4 163.2,43.6 171.4,40.1 C171.4,40.1 176.1,42.5 178.8,56.2 C183.1,58.6 187.2,61.8 190.9,65.4 C194.5,69.0 197.7,73.2 200.1,77.6 C213.8,80.2 216.3,84.9 216.3,84.9 C212.7,93.1 206.9,96.0 205.4,96.6 C205.1,102.4 203.0,107.8 198.3,112.5 C181.9,128.9 168.3,122.5 157.7,114.1 C157.9,116.9 156.7,120.9 152.7,124.9 L141.0,136.5 C139.8,137.7 141.6,141.9 141.8,141.8 Z" fill="currentColor" class="octo-body"></path></svg></a>

</div>
<div style="height: 3px; display: block; background-color: #1a6ecc; margin-top: -10.5px"></div>
<div class="jumbotron">
<div class="container-fluid main-container">
<h2 class="text-center">Discover the best <strong>templates</strong> for your <strong class="text-primary">R Markdown</strong> documents</h2>
<div class="row" style="margin-top: 50px">
<div class="col-sm-2"></div>
<div class="col-sm-4">
<div class="text-justify">
<a href="gallery.html" class="btn btn-success btn-lg btn-block"><i class="fa fa-search"></i> Explore</a><br>
<p style="font-size: 18px;">Check out existing `r nrow(cran_meta)+nrow(github_meta)` R markdown templates on CRAN or github and browse some pre-rendered outputs in the <a href="gallery.html">gallery</a>. </p>
</div>
</div>
<div class="col-sm-4">
<div class="text-justify">
<a href="https://github.com/rmdtemplates/rmdtemplates.github.io/edit/master/metadata/github.csv" class="btn btn-info btn-lg btn-block"><i class="fa fa-pencil-square-o"></i> Contribute</a><br>
<p style="font-size: 18px;">Submit your github template package by modifying this list and fire a pull request. </p>
</div>
</div>

</div>
</div>
</div>

<div class="container-fluid main-container">


